---
classoption: report
documentclass: uncdissertation
fontsize: 12pt
bibliography: includes/bib/lit-review.bib
output:
  pdf_document:
    includes:
      fig.caption: true
      before_body: includes/tex/doc_prefix_unc.tex
      in_header: includes/tex/header-unc.tex
    keep_tex: yes
    number_sections: yes
    pandoc_args:
    - --filter
    - C:/Python27/Scripts/pandoc-eqnos.exe
    toc: no
---


```{r include=FALSE}
#csl: includes/scripts/vancouver-authoryear.csl
#link-citations: yes

library(knitr)
library(kableExtra)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

<!-- NOTES: 

1. Some template code for formatting based on work from https://github.com/jvcasill/ua_thesis_rmd. All LaTeX code is copied from https://github.com/mmalahe/unc-dissertation including the .cls file.

2. Be careful of unicode characters, especially in the bibliography file. Very hard to find and can kick up errors that prevents the file from compiling. For example, a U+2AB unicode character that was not recognized and kept the program from compiling. or 'Package inputenc Error: Unicode char α (U+3B1)', which was actually in a journal title in the .bib file. Dashes are also problematic. See header-unc.tex to avoid that problem and add characters with 'declareunicodecharacters'.

Using pandoc-eqnos python program in pandoc to number equations:  https://github.com/tomduck/pandoc-eqnos
-->

<!-- Include introductory chapters. Also includes watermark text. -->

<!-- =========================== -->
<!-- START MAIN MATTER HERE -->
<!-- =========================== -->

\chapter{\uppercase{Manuscript 1 --- Title here}}
\addcontentsline{toc}{chapter}{\uppercase{Chapter 1: Manuscript 1 --- Title here}}


```{r, child='./sections/ms1.Rmd', eval=T}
```

<!-- Include tables and figures for first manuscript -->

```{r, child='includes/scripts/paper1/tables-figs.Rmd', eval=T}
```

\chapter{\uppercase{Manuscript 2 --- Title here. Make this a very long title to demonstrate that the title is single spaced in the table of contents as required by the graduate school.}}
\addcontentsline{toc}{chapter}{\uppercase{Manuscript 2 --- Title here. Make this a very long title to demonstrate that the title is single spaced in the table of contents as required by the graduate school.}}

```{r, child='./sections/ms2.Rmd', eval=T}
```

<!-- Include tables and figures for first manuscript -->

```{r, child='includes/scripts/paper2/tables-figs.Rmd', eval=T}
```


<!-- Include references -->

\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}

\backmatter

<!-- Include appendices -->

\appendix

\chapter{\uppercase{Background for power calculations}}\label{app1}
\addcontentsline{toc}{chapter}{\uppercase{Appendix: Useful information}}

```{r, child='./sections/appendix.Rmd', eval=T}
```


\chapter*{REFERENCES}
\addcontentsline{toc}{chapter}{REFERENCES}
\printbibliography{}
